### 2015-02-04 article.tex
write alpha

The paper considers the routing courier delivery problem with the service time for which the discrete model was constructed and the calculation scheme based on metaheuristic algorithm. The efficiency  of the proposed algorithm‘s scheme has been tested on a large-scale problems, generated on the basis of different classes known model routing problems.

@@

%%%%%%%%%%%%%%% To define new section use a command \subsection
% We are defining "Introduction" here
\subsection{Introduction}
%%%%% Paragraph text. To separate paragraphs use empty lines.
In this study, we consider a static vehicle routing problem with time windows. This variant of the routing problem is a common problem in the courier delivery industry.

The resulting solution is a master plan that solves the problem, and takes into account the daily events that take place according to plan. We evaluated the model and strategy decisions through simulation of randomly generated test data and known problems.

@@

\begin{figure}[h]
	\hfil\includegraphics[height=4.0in]{images/scheme}\hfil
	\caption
	{
		Example of Routing Delivery Problem.
	}
	\label{aba:fig1}
\end{figure}

@@

Denote by $N_l(\vec{u^i},\vec{\phi^i},p)$ probabilistic edge that goes from a deterministic $N_l(\vec{u^i},\vec{\phi^i})$ as follows. Each vector $\vec{v} \in N_l(\vec{u^i},\vec{\phi^i})$ with probability $p$ included in the neighborhood $N_l(\vec{u^i},\vec{\phi^i},p)$ regardless of other points. Note that this set may be empty or contain only one point. The General scheme of the probabilistic search algorithm with a list of prohibitions referred to as pseudo-code.

@@

\begin{algorithm}[H]
	\textbf{function TabuSearch}($u^0,l,p,h$) \\
	// Initialize variables:	\\
	$u^{opt} = u^0$;
	$F^{opt} = F^0$;
	$\phi^{0} =  \emptyset$;
	$i=0$; \\
	\While{the breakpoint is not triggered }{
	   $N_l = N_l(u^i,\phi^i,p,h) $; \\
		\eIf{$N_l \ne   \emptyset $}{
			$ u^{i+1} = u^i; i = i + 1;$ \\
			\textbf{continue;}
		}
		{
			// find optimum into the neighbord $N_l$: \\
			$ u^{i+1} : F(u^{i+1}) = min\{ F(y): y \in N_l \}$;
		}

		\If{$F(u^{i+1}) < F_{opt})$}{
			$ F_{opt} = F(u^{i+1})$;
			$ u^{opt} = u^{i+1}$;
		}

		$\phi^{i+1} = update(\phi^i)$;\\
		i = i + 1;\\

	}
	\textbf{return} $u^{opt}$;

@@

\subsubsection{The optimization of the algorithm parameters}

From these solutions generated population. To do this, first sort by the value of the objective function in ascending order. Each solution gets into the population with a given probability, the probability of selection decreases with increasing atomic number. It then crosses the decisions by the following rule: the first solution is randomly selected route, then the other solutions chosen a route that does not include the customer first route, etc. Other clients added by Solomon in the selected route. Then the process is repeated.

@@

@@

\begin{figure}[h]
	\hfil\includegraphics[height=3.0in]{images/tabuSize_stepCount}\hfil
	\caption
	{
	  The dependence of the quality of solutions on the size of the tabu list when using $ StepCount $ termination strategy
	}
	\label{aba:fig1}
\end{figure}

As should have been expected, for large values of the parameter a jam occurs in local optimum due to the large number of restrictions of movement in space. Otherwise if you select a too small tabu size, algorithm can still get stuck in a local optimum. 
\begin{figure}[h]
	\hfil\includegraphics[height=2.0in]{images/tabuSize_time}\hfil
	\caption
	{
	  The dependence of the quality of solutions on the size of the tabu list when using $ TimeMillisSpent $ termination strategy
	}
	\label{aba:fig1}
\end{figure}

In the second experiment we built a relationship between the number $N_{neighbors}$ of viewed solutions neighborhood $N_l(\vec{u})$ using $TimeMillisSpent$ termination strategy. 
\begin{figure}[h]
	\hfil\includegraphics[height=2.0in]{images/acceptedCountLimit}\hfil
	\caption
	{
	  The dependence of the quality of solutions on the neighborhood size when using $ TimeMillisSpent $ termination strategy
	}
	\label{aba:fig1}
\end{figure}

@@

@@

	\textbf{function constructSolution}( $U^{opt}, p_u, n^{min}_s$) \\
	// $U^{opt}$ -- an ordered set of optimal solutions \\

	\If{$ sizeof(U^{opt}) <  n^{min}_s$}{
		// construct solution using heuristics(for example, Solomon alg.)\\
		$u^0 = heuristicsConscruction();$
		return $u^0$;
	}

	\While{$i < sizeof(U^{opt})$}{
		\If{$random(0.0,1.0) > p^i_u$}{
		   i = i + 1; \\
		   goto 7;
		}
		$R = $randomly select a route from $u^{opt}_i$ solution;
		$u^0 = u^0 \cup R$;
		i = i + 1;\\

	}
	\textbf{return} $u^0$;

@@

Let $\vec{\psi_i} = (\psi^1_i,\psi^2_i,\psi^3_i) = (\tilde{l_i},\tilde{p_i},\tilde{l_h})$ -- a set of values of TabuSearch configuration parameters which was using for solving the problem in the step $i$.

Let $[\psi^j_{begin}, \psi^j_{end}]$ -- an optimal interval of the TabuSearch $j$ -parameter. (For example: if $j=3$, then: $[\psi^31_{begin}, \psi^3_{end}]= [h_{begin}, h_{end}] = [10, 40] $). These intervals are initial data and they are set in the initialization block.

@@

	$\psi = \emptyset$;
	$p_u = \emptyset$;
	$U^{opt} = \emptyset$;
	$i=0$; \\

	\While{the breakpoint is not triggered }{
		// set TabuSearch parameters \\
		\For{$j=1..3$}{
	  	// $f_j$ -- the density distribution of the random \\
	  	// variable $\psi^j$ (TabuSearch parameter $l,p $ or $ h$) \\
	  	$\psi^j_i = random(\psi^j_{begin}, \psi^j_{end}, f_j); $
	  	}

@@

		// Improve solution $u^0$ using TabuSearch algorithm 
		$u^{opt}_i = TabuSearch(u^0, \vec{\psi_i});$ \\

		$U^{opt}  = U^{opt} \cup \{u^{opt}_i\};$ \\

		// Sort ascending optimums $U$ of the objective function \\
		$U^{opt} = sort(U^{opt});$\\
		$p^{i+1}_u = update(p^i_u)$;\\

		i = i + 1;\\

	}
	\textbf{return} $u^{opt}_1$;

@@

\subsection{Conclusion}
In the process, has been studied and implemented tabu search algorithm to solve the static problem with time constraints. Modification of the algorithm to optimize the computational scheme. Modified algorithm gave the best solutions in terms of the balance between the number of vehicles and the distance traveled. such a feature of this algorithm can be used for decision support in intelligent systems. In practice, the more advantageous to use more vehicles if this will reduce the time to use them, this will reduce fuel costs and depreciation of transport;

The analysis of the parameters of implemented algorithms allowed us to determine their optimal values for this class of routing problems. With the modified algorithm was found solutions of model problems, which in most cases have an acceptable deviation from the global optimum;

@@

@@

@@

\bibitem{Assignment_Problems} E.~Rainer, Assignment problems, 2009, 402 p.

@@

\bibitem{problems_Christofides}  N. Christofides, S. Eilon, An algorithm for the vehicle dispatching problem //Operational Research Quarterly, 20, 1969, p. 309–318.
\bibitem{problems_Golden}  B. Golden, E. Wasil, J. Kelly, I-M. Chao. The impact of metaheuristics on solving the vehicle routing problem: Algorithms, problem sets, and computational results. In T. Crainic and G. Laporte, editors // Fleet Management and Logistics, Kluwer, Boston, 1998 p. 33–56.
\bibitem{problems_Taillard}  E. Taillard. VRP benchmarks.\\ http://mistic.heig-vd.ch/taillard/problemes.dir/vrp.dir/vrp.html, 1993.
\end{thebibliography}

>>>>

The paper considers the routing courier delivery problem with the service time for which the discrete model was constructed and the calculation scheme based on tabu search algorithm. The efficiency  of the proposed algorithm‘s scheme has been tested on a large-scale problems, which were generated on the basis of different classes known model routing problems.

@@

%%%%%%%%%%%%%%% To define new section use a command \subsection
% We are defining "Introduction" here
\subsection{Introduction}
%%%%% Paragraph text. To separate paragraphs use empty lines.
In the research we consider a static vehicle routing problem with time windows. This variant of the routing problem is a common problem in the courier delivery industry. Effective solution to this problem affects the quality of services provided by the company, as well as the magnitude of potential losses caused by the excess of the agreed terms of delivery. The proposed solution to the problem is based on the automation of the process of planning the route and involves the use of distributed information systems for the possible implementation of these approaches in practice. Another important criterion for good transport plan are low transport costs, which affect the cost of services.

The Routing Courier Delivery Problem with time windows requires that a set of vehicles satisfy a collection of customer requests. Each client request requires the use of a single vehicle to receive and load a specified amount of goods at one source location(sender) and to deliver them to destination location(receiver). All requests must be performed without violating either the vehicle capacity or the customer time window. The solution is a master plan that solves the problem, and takes into account the daily events that take place according to plan. In this paper, we present a discrete model and a modified tabu search algorithm  to solve the  Courier Delivery Problem with time windows.

In order to validate our strategies decisions technique effectiveness, we have constructed a new set of benchmark problems for the pickup and delivery problem with time windows based on which were generated on the basis of different classes known model routing problems. Computational results substantiate the solution quality and efficiency of our modified tabu search algorithm.

@@

\begin{figure}[h]
	\hfil\includegraphics[height=4.0in]{images/scheme}\hfil
	\caption
	{
		Example of the Routing Delivery Problem.
	}
	\label{aba:fig1}
\end{figure}

@@

\begin{algorithm}[H]
	\textbf{function TabuSearch}($u^0,l,p,h$) \\
	// Initialize variables:	\\
	$u^{opt} = u^0$
	$F^{opt} = F^0$
	$\phi^{0} =  \emptyset$
	$i=0$ \\
	\While{the breakpoint is not triggered }{
	   $N_l = N_l(u^i,\phi^i,p,h) $ \\
		\eIf{$N_l \ne   \emptyset $}{
			$ u^{i+1} = u^i$ \\
			$i = i + 1$ \\
			\textbf{goto} 5
		}
		{
			// find optimum into the neighbord $N_l$: \\
			$ u^{i+1} : F(u^{i+1}) = min\{ F(y): y \in N_l \}$
		}

		\If{$F(u^{i+1}) < F_{opt})$}{
			$ F_{opt} = F(u^{i+1})$ \\
			$ u^{opt} = u^{i+1}$
		}

		$\phi^{i+1} = update(\phi^i)$\\
		i = i + 1\\

	}
	\textbf{return} $u^{opt}$

Denote by $N_l(\vec{u^i},\vec{\phi^i},p)$ probabilistic edge that goes from a deterministic $N_l(\vec{u^i},\vec{\phi^i})$ as follows. Each vector $\vec{v} \in N_l(\vec{u^i},\vec{\phi^i})$ with probability $p$ included in the neighborhood $N_l(\vec{u^i},\vec{\phi^i},p)$ regardless of other points. Note that this set may be empty or contain only one point. The General scheme of the probabilistic search algorithm with a list of prohibitions referred to as pseudo-code in algorithm \\
scheme \ref{alg:TabuSearch}.

@@

@@

@@

\begin{figure}[h]
	\hfil\includegraphics[height=3.0in]{images/tabuSize_stepCount}\hfil
	\caption
	{
	  The dependence of the quality of solutions on the size of the tabu list when using $ StepCount $ termination strategy
	}
	\label{aba:fig2}
\end{figure}

@@

As should have been expected, for large values of the parameter a jam occurs in local optimum due to the large number of restrictions of movement in space. Otherwise if you select a too small tabu size, algorithm can still get stuck in a local optimum. 
\begin{figure}[h]
	\hfil\includegraphics[height=2.0in]{images/tabuSize_time}\hfil
	\caption
	{
	  The dependence of the quality of solutions on the size of the tabu list when using $ TimeMillisSpent $ termination strategy
	}
	\label{aba:fig3}
\end{figure}

In the second experiment we built a relationship between the number $N_{neighbors}$ of viewed solutions neighborhood $N_l(\vec{u})$ using $TimeMillisSpent$ termination strategy. 
\begin{figure}[h]
	\hfil\includegraphics[height=2.0in]{images/acceptedCountLimit}\hfil
	\caption
	{
	  The dependence of the quality of solutions on the neighborhood size when using $ TimeMillisSpent $ termination strategy
	}
	\label{aba:fig4}
\end{figure}

@@

We proceed to the description of the algorithm in scheme \ref{alg:constructSolution}. Let $U^{opt}$ is a sorted array of optimal solutions by value of the objective function ascending,  ie:
\begin{equation} \label{u_sorted}
F(u^{opt}_1) \leq F(u^{opt}_2) \leq \ldots < F(u^{opt}_i) \leq \ldots \leq F(u^{opt}_{sizeof(U^{opt})})
\end{equation}
Each solution $u^{opt}_i$ gets into the population with a given probability $p^i_u$, the probability of selection decreases with increasing sequence number:
\begin{equation} \label{p_sorted}
p^1_u = 1 > p^2_u > \ldots > p^i_u> \ldots   > p^{sizeof(U^{opt})}_u,  p^{sizeof(U^{opt})}_u > 0
\end{equation}

@@

	\textbf{function constructSolution}( $U^{opt}, p_u, n^{min}_s$) \\
	// $U^{opt}$ -- a sorted set array optimal solutions \\

	\If{$ sizeof(U^{opt}) <  n^{min}_s$}{
		// construct solution using heuristics(for example, Solomon alg.)\\
		$u^0 = heuristicsConscruction()$ \\
		\textbf{return} $u^0$
	}

	\While{$i < sizeof(U^{opt})$}{
		\If{$random(0.0,1.0) > p^i_u$}{
		   i = i + 1 \\
		   \textbf{goto} 8
		}
		$R_i = $randomly select a route from $u^{opt}_i$ solution;
		$u^0 = u^0 \cup R_i$
		i = i + 1\\

	\If{$u^0 is not complete$}{
	   	$u^0 = heuristicsConscruction(u^0)$
	}

	\textbf{return} $u^0$

@@

It then crosses solutions by the following rule: with the first solution is randomly selected route $R_1$. Then another solution is selected from a route $R_2$ that does not include client requests from the first  route etc. If the client requests were not included in the solution $u^0$, then these requests are added by the construction heuristics algorithm (for example, Solomon algorithm).

Now we describe the primary function $SolveCDP()$ of the modified algorithm presented in pseudocode form in Scheme \ref{alg:modTabuSearch}. In this function using a loop is a sequential formation of an array of the best solutions $U^{opt}$ by means TabuSearch algorithm.

Based on the results of the experiments described in the preceding section, we decided to set the parameters of the algorithm are not fixed values, but as a random variable of predetermined period. For example, the size of the tabu list $h$ is defined as the interval $[10,35]$(see pict. \ref{aba:fig2} and  pict. \ref{aba:fig3}) and the neighbordhood size $l=N_{neighbordhood}$ is defined as the interval $[600\cdot n,850\cdot n]$, where $n$ -- problem size (see pict. \ref{aba:fig4} ).

Let $\vec{\psi_i} = (\psi^1_i,\psi^2_i,\psi^3_i) = (\tilde{l_i},\tilde{p_i},\tilde{l_h})$ -- a set of values of the TabuSearch configuration parameters which was using for solving the problem in the step $i$.

Let $[\psi^j_{begin}, \psi^j_{end}]$ -- an optimal interval of the TabuSearch $j$ -parameter. (For example: if $j=3$, then: $[\psi^3_{begin}, \psi^3_{end}]= [h_{begin}, h_{end}] = [10, 40] $). These intervals are initial data and they are set in the initialization block.

The configuration parameters  $\psi^j_i $ are randomly selected from the interval $[\psi^j_{begin}, \psi^j_{end}]$ according to a distribution law. We proposed to build the distribution density $f_j(\psi^j_i)$ of the random variable $\psi^j_i$ as follows. At first, we define anchor points:

 \begin{equation} \label{anchor_points}
     \rho^j_i =  \dfrac{F(u^{opt}_1)}{avg[F(u^{opt}_k)]}, \forall k: \psi^j_k = \psi^j_i
 \end{equation}
 The number of anchor points $n_{\rho}$  is smaller than the set of optimal solutions, because a set of reference anchor points are removed the same point $(n_{\rho} \leq  n_u)$.

The main idea is that the distribution density should be larger at those points (parameters $\psi^j_i$) in which high quality solutions than the points at which the low quality of solutions.
Therefore, we presented the distribution function $f_j(z)$ as a sum of kernel functions:
 \begin{equation} \label{dist_density}
 f_j(z) = \alpha_j * \sum\limits_{i=1}^{n_{\rho}}  \rho^j_i * K(z -  \psi^j_i)
 \end{equation}
 where: $K(x)$ -- kernel function, $ \alpha$ -- a normalizing parameter

 We have chosen as the kernel the function of parabolic type(known as an Epanechnikov function),  because during the experiments the best results were obtained using this function:
 \begin{equation} \label{dist_density}
  K(z) = 3/4 \cdot (1-z^2)
 \end{equation}

@@

	$\psi = \emptyset$,
	$p_u = \emptyset$,
	$U^{opt} = \emptyset$,
	$i=0$ \\

	\While{the breakpoint is not triggered }{
		// set TabuSearch parameters \\
		\For{$j=1 \ldots 3$}{
	  	// $f_j$ -- the density distribution of the random \\
	  	// variable $\psi^j$ (TabuSearch parameter $l,p $ or $ h$) \\
	  	$\psi^j_i = random(\psi^j_{begin}, \psi^j_{end}, f_j) $
	  	}

@@

		// Improve solution $u^0$ using TabuSearch algorithm 
		$u^{opt}_i = TabuSearch(u^0, \vec{\psi_i})$ \\

		$U^{opt}  = U^{opt} \cup \{u^{opt}_i\}$ \\

		// Sort ascending optimums $U$ of the objective function \\
		$U^{opt} = sort(U^{opt})$\\
		$p^{i+1}_u = update(p^i_u)$\\

		i = i + 1\\

	}
	\textbf{return} $u^{opt}_1$

@@

 The parameter $\alpha_j$ was introduced in the density function to perform the normalization condition:
 \begin{equation} \label{norm_cond}
 \int\limits_{\psi^j_{begin}}^{\psi^j_{end}} f_j(z)dz = 1  =>  (\alpha_j)^{-1} = \sum\limits_{i=1}^{n_{\rho}} \rho^j_i \cdot  \int\limits_{\psi^j_{begin}}^{\psi^j_{end}} K(z -  \psi^j_i) dz 
 \end{equation}

 The parameter $\alpha_j$ can be written in explicit form:
  \begin{equation} \label{norm_cond}
 \begin{split}
 (\alpha_j)^{-1} & = \dfrac{3}{4} \cdot \sum\limits_{i=1}^{n_{\rho}} \rho^j_i \cdot [(1 - (\psi^j_i)^2) \cdot (\psi^j_{end} - \psi^j_{begin}) + \\
 & + \psi^j_i \cdot ((\psi^j_{end})^2 - (\psi^j_{begin})^2) - 1/3 \cdot (\psi^j_{end})^3 - (\psi^j_{begin})^3)]
 \end{split}
 \end{equation}

 In figure \ref{aba:fig5} the results of an experiment in which  were presented a dependence of the quality of the solutions obtained by the classical and modified algorithms and  the breaking point time. As seen from the graph, with an increase in operating time of the computational scheme, the quality of solutions obtained using the modified algorithm is growing faster than using classical Tabu Search algorithm.

 \begin{figure}[h]
 	\hfil\includegraphics[height=2.0in]{images/acceptedCountLimit}\hfil
 	\caption
 	{
 		The dependence of the quality of solutions and  the breaking point time using $ TimeMillisSpent $ termination strategy
 	}
 	\label{aba:fig5}
 \end{figure}

\subsection{Conclusion}
During the research has been investigated and implemented tabu search algorithm to solve the Static Routing Courier Delivery problem with time constraints. Also a modified algorithm was developed  based on the Tabu Search algorithm to improve the quality of the solutions. Modified algorithm gave the best solutions in terms of the balance between the number of vehicles and the cost traveled.  In practice this algorithm can be used for decision support in intelligent systems for improving the quality of customer service and for reducing waiting the time to use vehicle, this will reduce fuel costs and depreciation of transport.

The analysis of the parameters of implemented algorithms allowed us to determine their optimal values for this class of routing problems. With the modified algorithm was found solutions of model problems, which in most cases have an acceptable deviation from the global optimum.

@@

\bibitem{RCDS} F.~Ordonez, Chen Wang, A New Approach for Routing Courier Delivery Services //METRANS Transportation Center:University of Southern California
Los Angeles,  2012, 81--115.

@@

\bibitem{DELIVERY_2000} W~Barnes, Solving the pickup and delivery problem with time windows using reactive tabu search // Transportation Research Part B: Methodological, Vol. 34 Issue 2, 2000, p. 107--121.
% http://www.sciencedirect.com/science/article/pii/S0191261599000168

@@

@@

\bibitem{problems_Christofides}  N. Christofides, S. Eilon, An algorithm for the vehicle dispatching problem //Operational Research Quarterly, 20, 1969, p. 309–318.

\bibitem{problems_Golden}  B. Golden, E. Wasil, J. Kelly, I-M. Chao. The impact of metaheuristics on solving the vehicle routing problem: Algorithms, problem sets, and computational results. In T. Crainic and G. Laporte, editors // Fleet Management and Logistics, Kluwer, Boston, 1998 p. 33–56.

\bibitem{problems_Taillard}  E. Taillard. VRP benchmarks.\\ http://mistic.heig-vd.ch/taillard/problemes.dir/vrp.dir/vrp.html, 1993.
\end{thebibliography}
